Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Oxford comma
Roman maximum

\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}
\newcommand{\minimise}{\mathrm{minimise}}

@@

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
& \sigma.\maxImbalance = \sigma.maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
& \maxImbalance = maximum(\imbalance) \label{balAllB} \\
& \minimise(\maxImbalance) \label{balAllC}
\end{flalign}

@@

\section*{Acknowledgments}
We would like to thank our parents, God and all his angels.
\coffee{2}

>>>>

\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}
\newcommand{\minimise}{\mathrm{minimise}}
\newcommand{\maximum}{\mathrm{maximum}}

@@

\begin{flalign}
    & \forall_{i\in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] \in \{0,1\} \label{posA} \\
    & \forall_{i \in [0..m-1]} ~ \forall_{j \in [0..f-1]} ~ \sigma.\position[{i,j}] = 1 \iff \sigma.\timeSlot[{m.j+i}] \geq 0 \label{posB} \\
    & \forall_{i \in [0..m-1]} ~ \imbalance[{i}] = \abs*{\frac{n-1}{m} - \sum_{j=0}^{f-1} \position[{i,j}]} \label{imbA} \\
    & \sigma.\maxImbalance = \maximum(\sigma.imbalance)  \label{imbB}
\end{flalign}

@@

\begin{flalign}
    & \forall_{i \in [0..n-1]} ~ \imbalance[{i}] = \sigma[{i}].\maxImbalance \label{balAllA} \\
& \maxImbalance = \maximum(\imbalance) \label{balAllB} \\
& \minimise(\maxImbalance) \label{balAllC}
\end{flalign}

@@

\section*{Acknowledgments}
We would like to thank our parents, God, and all his angels.
\coffee{2}
